---
title: "Analysis of the difference between official appearance rate and player experience in Arknights"
author: "Tong Li"
date: "2020-12-22"
output: pdf_document
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE}
library("tidyverse")
data <- read.csv("arknights.csv")
data <- data %>% select(num_total_op, num_total_6op, account_level, num_limit_op, num_up, banner, server_region)
data <- data %>% mutate(pull_get_lim = ifelse(num_limit_op == 0,
                                         yes = 0, no = num_total_op/num_limit_op))
data <- data %>% mutate(prob_6str = num_total_6op / num_total_op)
data <- data %>% mutate(prob_lim = num_limit_op / num_total_op)
data <- data %>% filter(pull_get_lim != 0)
data <- na.omit(data)
attach(data)
```

## Abstract
  The game experience of players is a very important aspect for game companies,
however, the uncertain factor of operator pulling probability will being 
affected game experience of players. Pulling special banner in the Arknights 
always has the player to report spending a lot of resources still cannot get the
operator that wants. This analysis is based on the actual extraction experience 
from the video Publisher to analyze whether the feelings of players are true. 
Are this survivor bias or be it truly different from the officially reported
probability? What is the factors that affect the probability? After script
simulation and multiple Linear Regression, the problems will discuss based on 
the results.

## Keywords

  Observational study, multiple linear regression model, Causal Inference, 
"Gacha" system, Arknights

## Introduction
  Arknights is a free mobile game that contains banner pulling mechanism, 
players can get game resources through banner pulling (game resources will be
referred to as the operator below). The number of operators increases over time,
and there is a rarity rating. The more star of an operator has, the harder it is
to gain (3 stars — 6 stars in the game). Banner can be divided into ordinary 
banner and special banner. All banners will have mechanism of increasing 
probability of special operators, and limit open time. A new operator added to 
an ordinary banner is still withdrawable after banner rotation*, but the limited
banner contains a 6-star limited operator which can no longer be obtained after 
the banner rotation. This mechanism makes players want to gain the limit 
operator, but the actual experience is inconsistent with the officially 
announced pulling probability. Players spend a lot of resources but cannot get
restricted operator, this gap caused dissatisfaction. And from the game open
service to now, there are a totals of three limited card pool, every time will
appear the same phenomenon. A number of players gave videos of themselves
drawing operators to show that their investment was not commensurate with the
return. The game experience of players affects the operation of the whole game
company.

  This analysis will be a two-sided analysis aim at Arknights, both from 
official appearance rate that game company given and player's experience, to see
whether the official appearance rate is matching with player's experience or 
not. If yes, then survivorship bias occurs, players only noticed the voices of 
a small number of people who did not gain; if not, game company is publishing
unrealistic appearance rate. It will calm the dissatisfaction of many players 
and help clear the name of the game company. In this study, a script will be 
used base on official banner pulling probability (by python). It is showing 
chance of getting at least one limited operator. And r/r studio will be used to 
find out the relation between account level and probability of gain limited
operator. Besides, real data was obtained from the hands of the players for
analysis, and different predictor (number of pull to get at least one limited
operator, account level, pull from which banner, total number of pulling 6 stars
operators and number of pulling limited operator) will used for analysis using
the multiple linear regression model, to see whether the players’ comprehensive
acquisition probability has linear relation between account level, since there 
is a statement that company will reduce the probability of high-level accounts.
The specific method is to use same script but player's experiment probability to
calculate at what time of pulls, player will get at least one limited operator. 
  
  Methodology section would contain process of data collection and explains on 
each variable that use in multiple linear regression model. Result would post 
on result section, further discussion about summary and conclusion of result,
weakness and next step would conclude on Discussion part. Bibliography is in
Reference part.
  
  
## Methodology
# Data
Data was collected manual from video publisher that specialized in video of 
game. I chose the video with more banner pulling times as the data, video with
target of extract multiple times of limited operator is the best choice. Data
contains 11 variables:
_id: unique identifier.
player_id: unique id of each account given by server.
num_total: total time counts of pulled out from banner.
num_total_6op: total number of 6 stars operator gain from banner.
num_limit_op: total number of limit operator gain from banner.
num_up6: total number of appearance rate up 6 stars operator gain from banner.
banner: limit operator's code name, a differentiate of each special banner. 
server_region: the server at different region, CN means mainland China,WW means 
               other region. Observed by language of the game interface.
account_level: the level of account that accounted.
date: date of video uploaded.

  All data was collected either by eye watching each video or summary by publisher at the end of video. 

  On one hand, the official appearance rates for three banner are as follows:

  3 stars Operators have a 40% chance to appear in a pull.
  4 stars Operators have a 50% chance to appear in a pull.
  5 stars Operators have a 8% chance to appear in a pull.
  6 stars Operators have a 2% chance to appear in a pull.
  For special banner, appearance rate up operators (one is limited, one is not)
accounts for 70% of the odds when pulling a 6 stars. If a 6 stars Operator does 
not appear after 50 pulls, each subsequent pull will increase the 6 stars 
Operators' rate by 2%, up to 100%.

  On the other hand, in multiple linear regression model, total number of 
pulling, total number of 6 stars operator gain, total number of appearance rate 
up 6 stars operator, total number of limited operator gain and account level are
predictor. After remove missing values, 81 remain observations are available to
access analysis. During cleaning process, probability of getting a 6 stars 
operator and probability of getting a limited operator are added into data by 
doing simple division method. It is because the analysis is focusing on 
probability, not specific occurrence time number. 

# Model
  By fitting multiple linear regression model and observing p-value, 

- | Estimate | P-Value |
------|:-----------:|:-----------:|
Intercept | 135.7553 | 0.00239 |
account_level | 0.3297 | 0.45024 |  
bannerRosmontis| -12.1299 | 0.49078 | 
bannerW | 3.2245 | 0.84271 |
bannerW | 7.4650 | 0.90233 | 
num_total_6op | 15.9935 | <0.0001 |
num_limit_op | -95.7584 | <0.0001 |
 
  Only p-value of intercept, number of total gain 6 stars operators and number 
of limited operators get are smaller than 0.05, which is significant. Others has 
no evidence against null hypothesis, $\beta$ = 0, so model would be:
 
$$\hat{y} = 135.76 + 15.99x_{total 6stars} -100.67x_{num_limit_op}$$

  Holding other variable unchanged, as one 6 stars operator get, number of 
pulling to get at least one limited operator will increase around 16 times. Also
holding other variable unchanged, as one limited operator get, number of pulling
to get at least one limited operator will decrease around 100 times.
```{r, include=FALSE, echo=FALSE, message=FALSE}
mlr_model <- lm(pull_get_lim ~ account_level + banner +  num_total_6op + num_limit_op, data = data)
summary(mlr_model)
```

## Results
```{r, echo=FALSE, message=FALSE}
res_lm = lm(pull_get_lim ~ account_level, data=data) 
plot(res_lm, 1, title("Residual plot of pulling time of one limited and Account level"))
```
  
  In Model section, account level is not significant with p-value that greater 
than 0.05. Residual vs. Fitted plot between account level and pulling time of
getting at least one limited operator shows a almost constant mean (red line). 
Thus, there is no linear relationship between account level and pulling time of 
at least one limited operator. Also no casual relation between account level 
and rate of get limited operator, since pulling time has a strong negative 
linear relation between appearance rate. The lower rate, the more pulling time. 

  In script, scatter plot is showing the chance of getting at least one limited
operator from 0% to 99% in range 0 pull to 400 pull. 

```{r, echo=FALSE, message=FALSE}
script <- read.csv("script .csv")
script %>% ggplot(aes(x = pull_time, y = prob_offi)) + geom_point()
```
  
  At the beginning, probability rises rapidly, and gradually flattens out after
more than 75%. There is a gap between 50 - 60 times pull, and outstrip 50% at 70
times pulling.
  
  Based on player's experiment, appearance rate up operators accounts for 65.7% 
of the odds when pulling a 6 stars. 6 stars Operators have a 3.4% chance to 
appear in a pull. After plug in the new rate found from player, scatter plot 
becomes below in range 0 pull to 330 pulls to reach 99% chance:

```{r, include=FALSE, echo=FALSE, message=FALSE}
#65.7
data <- data %>% mutate(prob_6star = num_up/num_total_6op)
mean(data$prob_6star)
#3.4
data <- data %>% mutate(rate_6star = num_total_6op/num_total_op)
mean(data $rate_6star)
```
```{r, echo=FALSE, message=FALSE}
script %>% ggplot(aes(x = pull_time, y = prob_player)) + geom_point()
```
  
  It has same distribution as above with smaller range, smoother distribution.
Outstrip 50% at 60 times pulling.

## Discussion
  Overall, Conclusions can be drawn after collecting data, cleaning data,
establishing multiple Linear Regression model, using script, and drawing plots.
Now what we know is there is no casual inference between account level and 
pulling time for at least one limited operator, chance for player to get one
limited operator has no huge difference between official announced.
  
  There is indeed survivor bias, and players pay too much attention to the
information that can't pull limited operators. Of course, only a small group of
those who have operator will show that they have, but those who haven't will get
together and discuss it under a post. Analysis shows player's data acquisition
rates are even higher than the official rates. With the same 99% gain rate, the
official rates pulling takes 400, and the player only needs 330. But the line 
of 50% has no huge difference, since both are 10 pulls for one count, 60 and 70 
have not that big difference. Company will give 10 pulls card each time after
special banner is opened to fill up the 10 pulls difference and make player's 
cost less.

# Weaknesses and Next Steps
  First, data size is small for a game probability analysis, there are only 81 
data available after cleaning, which is far from enough compared to the huge 
number of players, that is why I have to get the probability and then use script
to come to the conclusion. Normally, percentage of players after a fixed pulling
number who get limited operator, and keep increase pulling number to find
distribution. Second, 10 pulls for one count is rough rather than 1 pulls one 
count. Third, data is obtained entirely by watching video, and there may be 
unknown factors such as editing that influence the final result. This may also 
be the reason why player probability is higher than official. Fourth, game 
include 3 special banner in CN, but only one in WW. But I put all them together 
to analysis, separate them could be a batter choice. Also for 3 banner in CN, 
game company might make some changes in the next two pools. Therefore, this 
analysis is very one-sided and can only be used for reference

  In the future, the database can be gradually enriched through other channels, 
and the time factor can be added to explore whether the game's card pool 
mechanism will lead to an increase in the draw probability when the card pool 
is refreshed every day.



## References
1. official appearance rates - https://mrfz.fandom.com/wiki/Headhunting
2. WishIHadAComputer, script of chance of getting limited operator. 2020. -
https://www.reddit.com/r/arknights/comments/hz23mf/here_are_the_chances_of_you_
getting_nian_in_x/
3.script by WishIHadAComputer, 2020.- https://www.onlinegdb.com/rkswEC2xv
